A Recurrence

### 2014-12-05 draft.tex
Added subsection on Existence of Common Solutions

>>>>

\subsection{Existence of Common Solutions}

\begin{lemma} 
\label{ab} For $k\geq 1$
\begin{equation*}
\alpha_{k+1} = - \beta_{k}.
\end{equation*}
\end{lemma}
\begin{proof}
We will show this using induction. As a base case note that $\alpha_2 = -1 = \beta_1$, and $\alpha_3 = -n = \beta_2$. Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$
\begin{equation*}
\alpha_{m+1} = n \alpha_{m} - \alpha_{m-1}.
\end{equation*}
Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ and so 
\begin{equation*}
\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m},
\end{equation*}
as desired.
\end{proof}
Now if we want to choose an $n$ such that  $F(x,y)$ has period $p$, our choice of $n$ must solve the equations 
\begin{align*}
x^{\alpha_p} y^{\beta_p} = x^{1}y^{0} \\
x^{\alpha_{p+1}} y^{\beta_{p+1}} = x^{0}y^{1}.
\end{align*}
Or in other terms
\begin{align*}
\alpha_p &=1 \\
\beta_p &=0\\ 
\alpha_{p+1} &= 0 \\
\beta_{p+1} &= 1.
\end{align*}
However as shown in Lemma \ref{ab} above $\alpha_{p+1} = -\beta_p$, and so $\beta_p=0$ and $\alpha_{p+1} =0$ are the same equation.  We also know by the recurrence relation for $\beta$ that 
\begin{equation*}
\beta_{p+1} = n \beta_{p} - \beta_{p-1}.
\end{equation*}
Substituting $\alpha_p = -\beta_{p-1}$ and $\beta_{p}=0$ gives us 
\begin{equation*}
\beta_{p+1} = \alpha_p.
\end{equation*} 
Therefore we actually only need to find a value for $n$ which satisfies the two equations
\begin{align*}
\alpha_p &=1\\
\alpha_{p+1}&=0.
\end{align*}
